\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2017-10-26 document/XSGRB_sample.tex
Adding Kaspers plot
fix

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The sample we present here include spectroscopic observations of 86 
systems fulfilling our sample criteria of which 72 are afterglow spectra 
and 14 are observations of the underlying host galaxies. 
UPDATE THIS.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{acknowledgements}
JPUF, BMJ and DX acknowledge support from the ERC-StG grant EGGS-278202.  The
Dark Cosmology Centre is funded by the Danish National Research Foundation.  TK
acknowledges support by the European Commission under the Marie Curie
Intra-European Fellowship Programme in FP7.  AdUP acknowledges support by the
European Commission under the Marie Curie Career Integration Grant programme
(FP7-PEOPLE-2012-CIG 322307).  This work made use of data supplied by the UK
{\it Swift} Science Data Centre at the University of Leicester.  Finally, we
acknowledge expert support from the ESO staff at the Paranal and La Silla
observatories in obtaining these target of opportunity data.

This work made use of data supplied by the UK Swift Science Data Centre at the University of Leicester.
\end{acknowledgements}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=16cm]{figures/XSGRB_redshift.pdf}
	\caption{Redshift distribution of the XSGRB sample.}
	\label{fig:z}
\end{figure*}

@@
